Causal Distillation Trees

### 2024-09-10 causalDT-manuscript/notebooks/paper_figures.Rmd
adjust heatmap color palette

  plt_nsplits <- viz_results$`Number of Splits Plot` +
    ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
    viridis::scale_fill_viridis(
      begin = 0.15, end = 0.95, option = "magma", limits = c(0., 7)
    )
  plt_ntrees <- viz_results$`Number of Trees Plot` +
    ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
    viridis::scale_fill_viridis(
      begin = 0.15, end = 0.95, option = "magma", limits = c(0, 100)
    )
  plt <- patchwork::wrap_plots(
    plt_ntrees, plt_nsplits, nrow = 1
  ) +
    patchwork::plot_layout(
      axis_titles = "collect_y"
    ) &
    ggplot2::labs(
      x = "Variable"
    )

@@

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

  plt_nsplits <- viz_results$`Number of Splits Plot` +
    ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
    viridis::scale_fill_viridis(
      begin = 0.05, end = 1, option = "magma", limits = c(0., 7)
    )
  plt_ntrees <- viz_results$`Number of Trees Plot` +
    ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
    viridis::scale_fill_viridis(
      begin = 0.05, end = 1, option = "magma", limits = c(0, 100)
    )
  plt <- patchwork::wrap_plots(
    plt_ntrees, plt_nsplits, nrow = 1
  ) +
    patchwork::plot_layout(
      axis_titles = "collect_y"
    ) &
    ggplot2::labs(
      x = "Variable"
    )

@@
